Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-25 paper/aldebaran.tex
coda

>>>>

We therefore believe that either Eltanin~b is not a false positive, or if it is, that it is not a common type of false positive, and is unlikely to affect our certainty that Aldebaran~b is real. \citet{2018arXiv180105239H} offer an alternative to the pulsation hypothesis, that one `mode' is the stellar rotation and the other is the planetary signal; this does not seem implausible.
